Every Author as First Author

### 2023-03-28 paper.tex
LaTeX code

First, hovering over the stacked names should pop up a tooltip with the
authors listed in their original order.
%In practice, PDF viewers do not seem to display the tooltips for text that is
%also a link to the bibliography, so readers must click on the link and then
%hover over the name stack in the bibliography; hopefully this extra step
%will be unnecessary in the future.
This feature works on all desktop PDF viewers we have tested,
but does not work on mobile devices we tested
(probably because they lack a natural notion of ``hovering'').
Because tooltips and links are both types of PDF annotations, they would
conflict with each other if used together, so we had to remove hyperlinks
from names; the years remain clickable links to the bibliography.

@@

Listings \ref{lst:namestack} and \ref{lst:natbib}

\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}
\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}

>>>>

First, hovering over the stacked names should pop up a tooltip with the
authors listed in their original order.
%In practice, PDF viewers do not seem to display the tooltips for text that is
%also a link to the bibliography, so readers must click on the link and then
%hover over the name stack in the bibliography; hopefully this extra step
%will be unnecessary in the future.
This feature works on all desktop PDF viewers we have tested,
except Chrome%
\footnote{See \url{https://bugs.chromium.org/p/chromium/issues/detail?id=1122489}}%
, but does not work on mobile devices we tested
(probably because they lack a natural notion of ``hovering'').
Because tooltips and links are both types of PDF annotations, they would
conflict with each other if used together, so we had to remove hyperlinks
from names; the years remain clickable links to the bibliography.

@@

\lstinputlisting[float=*,caption={\LaTeX\ source code for \texttt{\textbackslash namestack}},label=lst:namestack]{namestack.tex}

Listing~\ref{lst:namestack} shows the main source code for this macro.
The main idea is to render each name (into a \TeX\ horizontal box),
and stack those boxes vertically (in a \TeX\ vertical box)
with a negative one-line vertical space in between consecutive boxes.
The example above effectively becomes:

\begin{center}
\begin{lstlisting}
\vbox{%
  \hbox{Erik Demaine}%
  \vskip-\baselineskip
  \hbox{Martin Demaine}%
}%
\end{lstlisting}
\end{center}

This main content gets wrapped in three additional components:
%
\begin{enumerate}
\item \lstinline|\texttransparent{0.666}{...}| (from \texttt{transparent.sty})
  to make the names semi-transparent at opacity $2/3$.
  The opacity can also be overridden via an optional argument, as in
  \lstinline|\namestack[0.9]{...}|.
\item \lstinline|\pdftooltip| (from \texttt{pdfcomment.sty})
  to add tooltips to the stack, with the original list of names.
\item \lstinline|\BeginAccSupp{...ActualText=...} ... \EndAccSupp|
  (from \texttt{accsupp.sty}) to override copy/paste behavior for the stack.
\end{enumerate}

Listing~\ref{lst:natbib} shows additional code necessary to support
name/year bibliographies via \texttt{natbib.sty}.  Specifically, we
automatically wrap the ``name'' portion of a citation in
\lstinline|\namestack| (so it should be written as a semicolon-separated list).
We also need to disable hyperlinks on the name portion of each citation,
to avoid covering the tooltip with another PDF annotation.

\lstinputlisting[float=*,caption={\LaTeX\ code providing additional support for \texttt{natbib.sty}},label=lst:natbib]{stack-natbib.tex}
